---
title: "Fan Experiment Analysis - extra"
author: "JD"
date: "2025-02-04"
output: html_document
---

```{r}
library(tidyverse)
library(tidybayes)
library(brms)
library(bayesplot)
```

```{r, include = FALSE}
testing_all <- read_csv("../csv_files/online_testing_all.csv")

testing_all$charcount <- nchar(testing_all$test_sentence)
```

```{r}
dotproduct <- read_csv("../csv_files/dotproducts_perword.csv")
actr <- read_csv("../csv_files/actr_activations_perword.csv")
print(dotproduct)
print(actr)


```


# Clean up data

Add information about fan size and fan type.

```{r}

# change rt from s into ms

testing_all$rt <- testing_all$rt * 1000

#testing_all <- testing_all %>% filter(rt > 0)

testing_all$fan <- ifelse(testing_all$fan_loc == 4 | testing_all$fan_pers == 4, 1, -1)
testing_all$type_fan <- NA
testing_all$type_fan <- ifelse(testing_all$fan == 0, 0, ifelse(testing_all$fan_pers == 4, 1, -1))
testing_all <- testing_all %>% group_by(test_sentence) %>% mutate(pers_word=as.character(strsplit(test_sentence, " ")[[1]][2]), loc_word=as.character(strsplit(test_sentence, " ")[[1]][6]))
testing_all$pp_num <- as.numeric(testing_all$pp_num)
testing_all$manipulated_fan <- ifelse(testing_all$pp_num %% 2 == 1, "location", "person" )
testing_all$pp_num <- as.character(testing_all$pp_num)
testing_all$fan_word <- ifelse(testing_all$manipulated_fan == "person", testing_all$pers_word, testing_all$loc_word)
testing_all$fan_foil <- ifelse(testing_all$condition == "target", 0, ifelse(testing_all$fan == 1, 1, -1))
testing_all$fan_target <- ifelse(testing_all$condition == "foil", 0, ifelse(testing_all$fan == 1, 1, -1))
testing_all$type_condition <- ifelse(testing_all$condition == "target", 1, -1)

print(testing_all, width=Inf)

```

Exclude unreasonably long and short trials.

```{r}
testing_all <- testing_all %>% filter(rt <= 90000 & rt > 200)

```

Exclude people with accuracy lower than 65 percent.

```{r}
testing_all <- testing_all %>% filter(rt > 0) # exclude rts that are 0
testing_all %>% group_by(pp_num) %>% summarize(accuracy = mean(correct)) %>% filter(accuracy <= 0.65)
testing_correct <-testing_all %>% filter(!(pp_num %in% c("43","65", "90"))) # excluding 43 and 65 because of low accuracy
testing_correct %>% group_by(pp_num) %>% summarize(accuracy = mean(correct))

testing_correct %>% group_by(fan_pers, fan_loc) %>% summarise(accuracy = mean(correct), se=sd(correct)/sqrt(length(correct)))

```

```{r}
hist(testing_correct$rt, xlim = c(0, 15000), breaks = 500)

```

Exclude trials slower than 8.3 seconds (3 sample sd away from the sample mean).

```{r}
mean(testing_all$rt) + 2 * sd(testing_all$rt)

testing_faster <- testing_all %>% filter(rt <= mean(testing_all$rt) + 2 * sd(testing_all$rt)) # keeping only trials with a rt below 3 st.d. away from the mean
testing_faster_correct <- testing_correct %>% filter(rt <= mean(testing_all$rt) + 2 * sd(testing_all$rt)) # keeping only trials with a rt below 3 st.d. away from the mean

summary(testing_faster_correct$rt)

length(testing_faster_correct$rt)/length(testing_all$rt)
length(testing_correct$rt)/length(testing_all$rt)
length(testing_faster_correct$rt)/length(testing_correct$rt)

```

# Merge data

We include the dot product + log5 (i.e., pmi, which relates to spreading activation) to individual target-context words.

```{r}

dotproduct$fan_word <- dotproduct$Word
dotproduct$pp_num <- dotproduct$List

dotproduct <- dotproduct %>% group_by(pp_num, fan_word) %>% summarise(pmi = mean(Dot_product) + log(5))

dotproduct$pp_num <- as.character(dotproduct$pp_num)

print(dotproduct)

merged_data <- inner_join(testing_faster_correct, dotproduct, by=c("fan_word", "pp_num"))

actr$fan_word <- actr$Word
actr$pp_num <- actr$List

actr <- actr %>% group_by(pp_num, fan_word) %>% summarise(actr = mean(ACT_R_activation), Location_fan=first(Location_fan))

# rescale activations, could also be for location and person separately
actr$actr <- scale(actr$actr)
#actr$actr[which(actr$Location_fan==TRUE)] <- scale(actr$actr[which(actr$Location_fan==TRUE)])
#actr$actr[which(actr$Location_fan==FALSE)] <- scale(actr$actr[which(actr$Location_fan==FALSE)])

actr$pp_num <- as.character(actr$pp_num)

print(actr)

merged_data <- inner_join(merged_data, actr, by=c("fan_word", "pp_num"))

print(merged_data)
```

We subset by target (because these dot products were calculated on trained target-context pairs, 
and only targets were trained).

```{r}

merged_data <- subset(merged_data, condition == "target")

# some quick checks using lme4
library(lme4)

m1 <- lmer(log(rt) ~ pmi + (1|pp_num) + (1|fan_word), data=merged_data)
print(summary(m1))

m2 <- lmer(log(rt) ~ pmi + fan + (1|pp_num) + (1|fan_word), data=merged_data)
print(summary(m2))

m2.1 <- lmer(log(rt) ~ actr + fan + (1|pp_num) + (1|fan_word), data=merged_data)
print(summary(m2.1))

m3 <- lmer(log(rt) ~ pmi + actr + fan + (1|pp_num) + (1|fan_word), data=merged_data)
print(summary(m3))
#resid(m1)

mbase <- lmer(log(rt) ~ fan + (1|pp_num) + (1|fan_word), data=merged_data)
print(summary(mbase))

m4 <- lm(resid(mbase) ~ pmi , data=merged_data)
print(summary(m4))

```

# Bayesian modeling

```{r}

priors <- c(
  prior(normal(0, 15), class = Intercept),
  prior(normal(0, 2), class = b),
  prior(normal(0, 2), class = sigma),
  prior(normal(0, 2), class = sd),
  prior(lkj(2), class = cor)
)

priors_binom <- c(
  prior(normal(0, 2), class = Intercept),
  prior(normal(0, 1), class = b),
  prior(normal(0, 1), class = sd),
  prior(lkj(2), class = cor)
)

modeling <- function(useddata, measure, effect, adaptdelta=FALSE) {

  if (adaptdelta==FALSE) {
fit_model <- brm(
    paste0(measure, "~ 1 + ",effect," + fan + (1 + fan|pp_num) + (1 + fan|fan_word) "),# or (1|pers_word) + (1|loc_word)
  data = useddata,
  family = shifted_lognormal(),
  prior = priors,
  iter = 3000,
  cores = 4
)
  } else {
fit_model <- brm(
    paste0(measure, "~ 1 + ",effect," + fan + (1 + fan|pp_num) + (1 + fan|fan_word)"),# or (1|pers_word) + (1|loc_word)
  data = useddata,
  family = shifted_lognormal(),
  prior = priors,
  control = list(adapt_delta = 0.95),
  iter = 3000,
  cores = 4
)
  }

# output of the model

fit_model

}

# full random effects structure

modeling_full <- function(useddata, measure, effect, adaptdelta=FALSE) {

  if (adaptdelta==FALSE) {
fit_model <- brm(
    paste0(measure, "~ 1 + ",effect," + fan  + (1 + fan|pp_num) + (1 + ",effect," + fan|fan_word)"),# or (1|pers_word) + (1|loc_word)
  data = useddata,
  family = shifted_lognormal(),
  prior = priors,
  iter = 3000,
  cores = 4
)
  } else {
fit_model <- brm(
    paste0(measure, "~ 1 + ",effect," + fan  + (1 + fan|pp_num) + (1 + ",effect," + fan|fan_word)"),# or (1|pers_word) + (1|loc_word)
  data = useddata,
  family = shifted_lognormal(),
  prior = priors,
  control = list(adapt_delta = 0.999),
  iter = 3000,
  cores = 4
)
  }

# output of the model

fit_model

}

modeling_binom <- function(useddata, measure, effect, adaptdelta=FALSE) {

  if (adaptdelta==FALSE) {
    fit_model <- brm(paste0(measure, "~ 1 + ",effect," + fan  + (1 + ",effect," + fan|pp_num) + (1 + ",effect," + fan|fan_word)"),
  data = useddata,
  family = "bernoulli",
  prior = priors_binom,
  iter = 3000,
  cores = 4
)
  } else {
fit_model <- brm(paste0(measure, "~ 1 + ",effect," + fan  + (1 + ",effect," + fan|pp_num) + (1 + ",effect," + fan|fan_word)"),
  data = useddata,
  family = "bernoulli",
  prior = priors_binom,
  control = list(adapt_delta = 0.95),
  iter = 3000,
  cores = 4
)
  }

# output of the model

fit_model

}


```

# Modeling

## Accuracy models

### Accuracy model 1

```{r}

#fan_accuracy <- modeling_binom(merged_data, "correct", adaptdelta = TRUE)
#save(fan_accuracy, file="../stan_models/fan_accuracy.Rdata")
load("../stan_models/fan_accuracy.Rdata")

print(fan_accuracy, digits=3)

```

```{r, fig.width=10, figh.height=8, fig.fullwidth=TRUE}

pp_check(fan_accuracy, ndraws=1000)

pp_check(fan_accuracy, ndraws=1000, type = "stat", stat = "mean")

```

## RT models

- using faster+correct subset
- only looking at dataset with RTs smaller than 10.8 s and accuracy higher than 60 per cent.

### RT model 1 - maximal working random effects

I removed pmi for ppnum because that model had problems to converge even after increased adapt delta and maxtreedepth.

```{r}
fan_together_full <- modeling_full(merged_data, "rt", "pmi", adaptdelta=TRUE)
save(fan_together_full, file="../stan_models/fan_together_full.Rdata")
load("../stan_models/fan_together_full.Rdata")

print(fan_together_full, digits=3)
```

```{r, fig.width=10, figh.height=8, fig.fullwidth=TRUE}

pp_check(fan_together_full, ndraws=1000)

pp_check(fan_together_full, ndraws=1000, type = "stat", stat = "mean")

pp_check(fan_together_full, ndraws=1000, type = "stat", stat = "median")

```

### RT model 2 - maximal working random effects

```{r}
fan_together_full_actr <- modeling_full(merged_data, "rt", "actr", adaptdelta=TRUE)
save(fan_together_full_actr, file="../stan_models/fan_together_full_actr.Rdata")
load("../stan_models/fan_together_full_actr.Rdata")

print(fan_together_full_actr, digits=3)
```

```{r, fig.width=10, figh.height=8, fig.fullwidth=TRUE}

pp_check(fan_together_full_actr, ndraws=1000)

pp_check(fan_together_full_actr, ndraws=1000, type = "stat", stat = "mean")

pp_check(fan_together_full_actr, ndraws=1000, type = "stat", stat = "median")

```
