---
title: "Experiment fan: posterior plots"
author: "JD"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r computetime,echo=FALSE}
time <- Sys.time()
```

`r time`

```{r packages,echo=FALSE,message = FALSE}

library(tidyverse)
library(readr)
library(here)
library(tidybayes)
library(brms)
library(bayesplot)

```

Prep functions.

```{r, message = FALSE}

draw_posteriors <- function(fit_model) {

    # collect posterior samples
    post_pars <- as_draws_df(fit_model) 

    pars <- c("b_Intercept", "b_pmi", "b_fan")

    plot_draws <- data.frame(.variable=c(rep("Intercept", length(post_pars$b_Intercept)), rep("DotProduct",  length(post_pars$b_Intercept)), rep("Fan",  length(post_pars$b_Intercept))), logms=c(post_pars[[pars[1]]], post_pars[[pars[2]]], post_pars[[pars[3]]]))

# Prepare the plot

  plot_draws

}

draw_posteriors2 <- function(fit_model) {

    # collect posterior samples
    post_pars <- as_draws_df(fit_model) 

    pars <- c("b_Intercept", "b_pmi")

    plot_draws <- data.frame(.variable=c(rep("Intercept", length(post_pars$b_Intercept)), rep("DotProduct",  length(post_pars$b_Intercept))), logms=c(post_pars[[pars[1]]], post_pars[[pars[2]]]))

# Prepare the plot

  plot_draws

}

draw_posteriors_actr <- function(fit_model) {

    # collect posterior samples
    post_pars <- as_draws_df(fit_model) 

    pars <- c("b_Intercept", "b_actr", "b_fan")

    plot_draws <- data.frame(.variable=c(rep("Intercept", length(post_pars$b_Intercept)), rep("ACT-R_approximations",  length(post_pars$b_Intercept)), rep("Fan",  length(post_pars$b_Intercept))), logms=c(post_pars[[pars[1]]], post_pars[[pars[2]]], post_pars[[pars[3]]]))

# Prepare the plot

  plot_draws

}

draw_posteriors_actr2 <- function(fit_model) {

    # collect posterior samples
    post_pars <- as_draws_df(fit_model) 

    pars <- c("b_Intercept", "b_actr")

    plot_draws <- data.frame(.variable=c(rep("Intercept", length(post_pars$b_Intercept)), rep("ACT-R_approximations",  length(post_pars$b_Intercept))), logms=c(post_pars[[pars[1]]], post_pars[[pars[2]]]))

# Prepare the plot

  plot_draws

}

```

# Figures

## Fan together full

This is the model that includes pmi and fan, using the formula:

`rt ~ 1 + pmi + fan + (1 + fan | pp_num) + (1 + pmi + fan | fan_word)`

```{r}

load("../stan_models/fan_together_full.Rdata")

print(fan_together_full, digits=3)

plot_draws <- draw_posteriors(fan_together_full)
    
g1 <- ggplot(subset(plot_draws, .variable != "Intercept"), aes(y=.variable, x=logms, fill=after_stat(x>0))) +
stat_halfeye(.width=.95, point_interval="mean_hdi", interval_size_range = c(1, 3))+
  geom_vline(xintercept = 0, linetype = "dashed") +
  guides(fill = "none") +
  labs(x="Log ms", y = NULL)+
  scale_fill_manual(values = c("grey40", "lightblue")) + theme_bw(30)



```

```{r, fig.width=10, figh.height=8, fig.fullwidth=TRUE}

g1

ggsave("../figures/skipgram-fan.png", width=10, height=7)

```


```{r, fig.width=10, fig.height=7, fig.fullwidth=TRUE}

testing_target <- read_csv("../csv_files/online_testing_modeled_data.csv") %>%
  mutate(pp_num = as.character(pp_num))

print(testing_target, n=10, width=Inf)
summary(testing_target$rt)

length(testing_target$pp_num)
length(fan_together_full$data[,1]) # these two lengths must match

model_data_fan_full <- bind_cols(testing_target %>% select(fan_loc, fan_pers, fan_target, rt_check=rt, fan_word_check=fan_word), fan_together_full$data) %>%
  mutate(pmi_value = ifelse(pmi < quantile(pmi)[2], "low", ifelse(pmi > quantile(pmi)[4], "high", NA)))

# checks that rt in model data and in testing target match; similarly for fan word
stopifnot(all(round(model_data_fan_full$rt_check) == round(model_data_fan_full$rt)))
stopifnot(all(model_data_fan_full$fan_word_check == model_data_fan_full$fan_word))

# predictions, put in the long table
yrep_full <- posterior_predict(fan_together_full, ndraws = 100)

pred_long_full <- as.data.frame(yrep_full) %>%
  mutate(draw = row_number()) %>%
  pivot_longer(-draw, names_to = "obs_id", values_to = "rt_pred") %>%
  mutate(obs_id = as.integer(sub("V", "", obs_id))) %>%
  left_join(model_data_fan_full %>%
              mutate(obs_id = row_number()) %>%
              select(obs_id, pp_num, fan_loc, fan_pers, fan_target, fan_word, pmi_value),
            by = "obs_id")

pred_long_full

pred_long_full %>% group_by(fan_target) %>% summarise(mean(rt_pred), median(rt_pred), sd(rt_pred))
pred_long_full %>% group_by(pmi_value) %>% summarise(mean(rt_pred), median(rt_pred), sd(rt_pred))

# fan_target (-1 / +1), all participants
ggplot() +
  geom_density(data = pred_long_full %>% mutate(source = paste0("pred_", fan_target)),
               aes(x = rt_pred, group = interaction(draw, fan_target), color = source), alpha = 0.3) +
  geom_density(data = model_data_fan_full %>% mutate(source = paste0("obs_", fan_target)),
               aes(x = rt, color = source), linewidth = 1) +
  scale_color_manual(values = c("obs_-1" = "darkblue", "pred_-1" = "lightblue",
                                "obs_1"  = "darkred",  "pred_1"  = "lightcoral"),
                     labels = c("obs_-1" = "observed fan 2", "pred_-1" = "predicted fan 2",
                                "obs_1"  = "observed fan 4", "pred_1"  = "predicted fan 4")) +
  guides(color = guide_legend(
    override.aes = list(
      fill = c("darkblue", "darkred", "lightblue", "lightcoral"),
      linewidth = 0,
      alpha = 1
    ))) +
  scale_x_continuous(limits = c(200, 6000)) +
  labs(x = "RT (ms)", color = NULL) +
  theme_bw(30) +
  theme(legend.position = c(0.75, 0.75))

ggsave("../figures/ppc-fan_together_full.png", width=10, height=7)

# pmi_value (low / high), all participants
ggplot() +
  geom_density(data = pred_long_full %>% filter(!is.na(pmi_value)) %>% mutate(source = paste0("pred_", pmi_value)),
               aes(x = rt_pred, group = interaction(draw, pmi_value), color = source), alpha = 0.3) +
  geom_density(data = model_data_fan_full %>%  filter(!is.na(pmi_value)) %>%mutate(source = paste0("obs_", pmi_value)),
               aes(x = rt, color = source), linewidth = 1) +
  scale_color_manual(values = c("obs_low"  = "darkgreen",  "pred_low"  = "lightgreen",
                                "obs_high" = "darkorchid", "pred_high" = "plum"),
                     labels = c("obs_low"  = "observed low pmi",  "pred_low"  = "predicted low pmi",
                                "obs_high" = "observed high pmi", "pred_high" = "predicted high pmi")) +
  guides(color = guide_legend(
    override.aes = list(
      fill = c("darkgreen", "darkorchid", "lightgreen", "plum"),
      linewidth = 0,
      alpha = 1
    ))) +
  scale_x_continuous(limits = c(200, 6000)) +
  labs(x = "RT (ms)", color = NULL) +
  theme_bw(30) +
  theme(legend.position = c(0.75, 0.75))

ggsave("../figures/ppc-fan_together_full-pmi_value.png", width=10, height=7)

boxplot_data <- bind_rows(
  pred_long_full %>%
    mutate(fan_target = factor(fan_target, levels = c(-1, 1), labels = c("fan 2", "fan 4"))) %>%
    select(rt = rt_pred, fan_target) %>% mutate(type = "predicted"),
  model_data_fan_full %>%
    mutate(fan_target = factor(fan_target, levels = c(-1, 1), labels = c("fan 2", "fan 4"))) %>%
    select(rt, fan_target) %>% mutate(type = "observed")
)

ggplot(boxplot_data, aes(x = fan_target, y = rt, fill = interaction(type, fan_target))) +
  geom_boxplot(position = position_dodge(0.8)) +
  scale_fill_manual(values = c("observed.fan 2"  = "darkblue",  "predicted.fan 2" = "lightblue",
                                "observed.fan 4"  = "darkred",   "predicted.fan 4" = "lightcoral"),
                    labels = c("observed.fan 2"  = "observed fan 2",  "predicted.fan 2" = "predicted fan 2",
                               "observed.fan 4"  = "observed fan 4",  "predicted.fan 4" = "predicted fan 4")) +
  scale_y_log10(limits = c(200, 6000)) +
  labs(x = NULL, y = "RT (ms)", fill = NULL) +
  theme_bw(30) +
  theme(legend.position = c(0.85, 0.85))

ggsave("../figures/boxplot-fan_together_full.png", width=10, height=7)

```


## Pmi model

This is the model with pmi only and intercept-only effects.

`rt ~ 1 + pmi + (1 | pp_num) + (1 | fan_word)`

```{r}

load("../stan_models/pmi_model.Rdata")

print(pmi_model, digits=3)

plot_draws <- draw_posteriors2(pmi_model)
    
g1 <- ggplot(subset(plot_draws, .variable != "Intercept"), aes(y=.variable, x=logms, fill=after_stat(x>0))) +
stat_halfeye(.width=.95, point_interval="mean_hdi", interval_size_range = c(1, 3))+
  geom_vline(xintercept = 0, linetype = "dashed") +
  guides(fill = "none") +
  labs(x="Log ms", y = NULL)+
  scale_fill_manual(values = c("grey40", "lightblue")) + theme_bw(30)

```

```{r, fig.width=10, figh.height=8, fig.fullwidth=TRUE}

g1

ggsave("../figures/skipgram.png", width=10, height=7)

```

```{r, fig.width=10, fig.height=7, fig.fullwidth=TRUE}

length(testing_target$pp_num)
length(pmi_model$data[,1]) # these two lengths must match

model_data_pmi <- bind_cols(testing_target %>% select(fan_loc, fan_pers, fan_target, rt_check=rt, fan_word_check=fan_word), pmi_model$data) %>%
  mutate(pmi_value = ifelse(pmi < quantile(pmi)[2], "low", ifelse(pmi > quantile(pmi)[4], "high", NA)))

model_data_pmi %>% group_by(fan_target) %>% summarise(mean(pmi), sd(pmi))
model_data_pmi %>% group_by(fan_target) %>% summarise(mean(rt), sd(rt))
model_data_pmi %>% group_by(pmi_value) %>% summarise(mean(rt), sd(rt))

summary(model_data_pmi$pmi)

quantile(model_data_pmi$pmi)[2]

stopifnot(all(round(model_data_pmi$rt_check) == round(model_data_pmi$rt)))
stopifnot(all(model_data_pmi$fan_word_check == model_data_pmi$fan_word))

yrep_full <- posterior_predict(pmi_model, ndraws = 100)
pred_long_full <- as.data.frame(yrep_full) %>%
  mutate(draw = row_number()) %>%
  pivot_longer(-draw, names_to = "obs_id", values_to = "rt_pred") %>%
  mutate(obs_id = as.integer(sub("V", "", obs_id))) %>%
  left_join(model_data_pmi %>%
              mutate(obs_id = row_number()) %>%
              select(obs_id, pp_num, fan_loc, fan_pers, fan_target, fan_word, pmi_value),
            by = "obs_id")

pred_long_full %>% group_by(pmi_value) %>% summarise(mean(rt_pred), sd(rt_pred))
pred_long_full %>% group_by(fan_target) %>% summarise(mean(rt_pred), sd(rt_pred))


# fan_target (-1 / +1), all participants
ggplot() +
  geom_density(data = pred_long_full %>% mutate(source = paste0("pred_", fan_target)),
               aes(x = rt_pred, group = interaction(draw, fan_target), color = source), alpha = 0.3) +
  geom_density(data = model_data_pmi %>% mutate(source = paste0("obs_", fan_target)),
               aes(x = rt, color = source), linewidth = 1) +
  scale_color_manual(values = c("obs_-1" = "darkblue", "pred_-1" = "lightblue",
                                "obs_1"  = "darkred",  "pred_1"  = "lightcoral"),
                     labels = c("obs_-1" = "observed fan 2", "pred_-1" = "predicted fan 2",
                                "obs_1"  = "observed fan 4", "pred_1"  = "predicted fan 4")) +
  guides(color = guide_legend(
    override.aes = list(
      fill = c("darkblue", "darkred", "lightblue", "lightcoral"),
      linewidth = 0,
      alpha = 1
    ))) +
  scale_x_continuous(limits = c(200, 6000)) +
  labs(x = "RT (ms)", color = NULL) +
  theme_bw(30) +
  theme(legend.position = c(0.75, 0.75))

ggsave("../figures/ppc-pmi_model.png", width=10, height=7)

# pmi_value (low / high), all participants
ggplot() +
  geom_density(data = pred_long_full %>% filter(!is.na(pmi_value)) %>% mutate(source = paste0("pred_", pmi_value)),
               aes(x = rt_pred, group = interaction(draw, pmi_value), color = source), alpha = 0.3) +
  geom_density(data = model_data_pmi %>%  filter(!is.na(pmi_value)) %>%mutate(source = paste0("obs_", pmi_value)),
               aes(x = rt, color = source), linewidth = 1) +
  scale_color_manual(values = c("obs_low"  = "darkgreen",  "pred_low"  = "lightgreen",
                                "obs_high" = "darkorchid", "pred_high" = "plum"),
                     labels = c("obs_low"  = "observed low pmi",  "pred_low"  = "predicted low pmi",
                                "obs_high" = "observed high pmi", "pred_high" = "predicted high pmi")) +
  guides(color = guide_legend(
    override.aes = list(
      fill = c("darkgreen", "darkorchid", "lightgreen", "plum"),
      linewidth = 0,
      alpha = 1
    ))) +
  scale_x_continuous(limits = c(200, 6000)) +
  labs(x = "RT (ms)", color = NULL) +
  theme_bw(30) +
  theme(legend.position = c(0.75, 0.75))

ggsave("../figures/ppc-pmi_model-pmi_value.png", width=10, height=7)

# boxplot: observed vs predicted for fan 2 and fan 4
boxplot_data <- bind_rows(
  pred_long_full %>%
    mutate(fan_target = factor(fan_target, levels = c(-1, 1), labels = c("fan 2", "fan 4"))) %>%
    select(rt = rt_pred, fan_target) %>%
    mutate(type = "predicted"),
  model_data_pmi %>%
    mutate(fan_target = factor(fan_target, levels = c(-1, 1), labels = c("fan 2", "fan 4"))) %>%
    select(rt, fan_target) %>%
    mutate(type = "observed")
)

ggplot(boxplot_data, aes(x = fan_target, y = rt, fill = interaction(type, fan_target))) +
  geom_boxplot(position = position_dodge(0.8)) +
  scale_fill_manual(values = c("observed.fan 2"  = "darkblue",  "predicted.fan 2" = "lightblue",
                                "observed.fan 4"  = "darkred",   "predicted.fan 4" = "lightcoral"),
                    labels = c("observed.fan 2"  = "observed fan 2",  "predicted.fan 2" = "predicted fan 2",
                               "observed.fan 4"  = "observed fan 4",  "predicted.fan 4" = "predicted fan 4")) +
  scale_y_log10(limits = c(200, 6000)) +
  labs(x = NULL, y = "RT (ms)", fill = NULL) +
  theme_bw(30) +
  theme(legend.position = c(0.85, 0.85))

ggsave("../figures/boxplot-pmi_model.png", width=10, height=7)

```

# Figures ACT-R

## Fan together full act-r

The model with act-r and fan. The formula:

`rt ~ 1 + actr + fan + (1 + fan | pp_num) + (1 + actr + fan | fan_word)`

```{r}

load("../stan_models/fan_together_full_actr.Rdata")

print(fan_together_full_actr, digits=3)

plot_draws <- draw_posteriors_actr(fan_together_full_actr)
    
g1 <- ggplot(subset(plot_draws, .variable != "Intercept"), aes(y=.variable, x=logms, fill=after_stat(x>0))) +
stat_halfeye(.width=.95, point_interval="mean_hdi", interval_size_range = c(1, 3))+
  geom_vline(xintercept = 0, linetype = "dashed") +
  guides(fill = "none") +
  labs(x="Log ms", y = NULL)+
  scale_fill_manual(values = c("grey40", "lightblue")) + theme_bw(30)



```

```{r, fig.width=10, figh.height=8, fig.fullwidth=TRUE}

g1

ggsave("../figures/actr-fan.png", width=10, height=7)

```

```{r, fig.width=10, fig.height=7, fig.fullwidth=TRUE}

model_data_actr_full <- bind_cols(testing_target %>% select(fan_loc, fan_pers, fan_target, rt_check=rt, fan_word_check=fan_word), fan_together_full_actr$data)

stopifnot(all(round(model_data_actr_full$rt_check) == round(model_data_actr_full$rt)))
stopifnot(all(model_data_actr_full$fan_word_check == model_data_actr_full$fan_word))

yrep_full <- posterior_predict(fan_together_full_actr, ndraws = 100)
pred_long_actr_full <- as.data.frame(yrep_full) %>%
  mutate(draw = row_number()) %>%
  pivot_longer(-draw, names_to = "obs_id", values_to = "rt_pred") %>%
  mutate(obs_id = as.integer(sub("V", "", obs_id))) %>%
  left_join(model_data_actr_full %>%
              mutate(obs_id = row_number()) %>%
              select(obs_id, pp_num, fan_loc, fan_pers, fan_target, fan_word),
            by = "obs_id")

ggplot() +
  geom_density(data = pred_long_actr_full %>% mutate(source = paste0("pred_", fan_target)),
               aes(x = rt_pred, group = interaction(draw, fan_target), color = source), alpha = 0.3) +
  geom_density(data = model_data_actr_full %>% mutate(source = paste0("obs_", fan_target)),
               aes(x = rt, color = source), linewidth = 1) +
  scale_color_manual(values = c("obs_-1" = "darkblue", "pred_-1" = "lightblue",
                                "obs_1"  = "darkred",  "pred_1"  = "lightcoral"),
                     labels = c("obs_-1" = "observed fan 2", "pred_-1" = "predicted fan 2",
                                "obs_1"  = "observed fan 4", "pred_1"  = "predicted fan 4")) +
  guides(color = guide_legend(
    override.aes = list(
      fill = c("darkblue", "darkred", "lightblue", "lightcoral"),
      linewidth = 0,
      alpha = 1
    ))) +
  scale_x_continuous(limits = c(200, 6000)) +
  labs(x = "RT (ms)", color = NULL) +
  theme_bw(30) +
  theme(legend.position = c(0.75, 0.75))

ggsave("../figures/ppc-fan_together_full_actr.png", width=10, height=7)

boxplot_data <- bind_rows(
  pred_long_actr_full %>%
    mutate(fan_target = factor(fan_target, levels = c(-1, 1), labels = c("fan 2", "fan 4"))) %>%
    select(rt = rt_pred, fan_target) %>% mutate(type = "predicted"),
  model_data_actr_full %>%
    mutate(fan_target = factor(fan_target, levels = c(-1, 1), labels = c("fan 2", "fan 4"))) %>%
    select(rt, fan_target) %>% mutate(type = "observed")
)

ggplot(boxplot_data, aes(x = fan_target, y = rt, fill = interaction(type, fan_target))) +
  geom_boxplot(position = position_dodge(0.8)) +
  scale_fill_manual(values = c("observed.fan 2"  = "darkblue",  "predicted.fan 2" = "lightblue",
                                "observed.fan 4"  = "darkred",   "predicted.fan 4" = "lightcoral"),
                    labels = c("observed.fan 2"  = "observed fan 2",  "predicted.fan 2" = "predicted fan 2",
                               "observed.fan 4"  = "observed fan 4",  "predicted.fan 4" = "predicted fan 4")) +
  scale_y_log10(limits = c(200, 6000)) +
  labs(x = NULL, y = "RT (ms)", fill = NULL) +
  theme_bw(30) +
  theme(legend.position = c(0.85, 0.85))

ggsave("../figures/boxplot-fan_together_full_actr.png", width=10, height=7)

```

## ACT-R model

The model with just actr.

`rt ~ 1 + actr + (1 | pp_num) + (1 | fan_word)`

```{r}

load("../stan_models/actr_model.Rdata")

print(actr_model, digits=3)

plot_draws <- draw_posteriors_actr2(actr_model)
    
g1 <- ggplot(subset(plot_draws, .variable != "Intercept"), aes(y=.variable, x=logms, fill=after_stat(x>0))) +
stat_halfeye(.width=.95, point_interval="mean_hdi", interval_size_range = c(1, 3))+
  geom_vline(xintercept = 0, linetype = "dashed") +
  guides(fill = "none") +
  labs(x="Log ms", y = NULL)+
  scale_fill_manual(values = c("grey40", "lightblue")) + theme_bw(30)

```

```{r, fig.width=10, figh.height=8, fig.fullwidth=TRUE}

g1

ggsave("../figures/actr.png", width=10, height=7)

```

```{r, fig.width=10, fig.height=7, fig.fullwidth=TRUE}

model_data_actr <- bind_cols(testing_target %>% select(fan_loc, fan_pers, fan_target, rt_check=rt, fan_word_check=fan_word), actr_model$data)

stopifnot(all(round(model_data_actr$rt_check) == round(model_data_actr$rt)))
stopifnot(all(model_data_actr$fan_word_check == model_data_actr$fan_word))

yrep_full <- posterior_predict(actr_model, ndraws = 100)
pred_long_actr <- as.data.frame(yrep_full) %>%
  mutate(draw = row_number()) %>%
  pivot_longer(-draw, names_to = "obs_id", values_to = "rt_pred") %>%
  mutate(obs_id = as.integer(sub("V", "", obs_id))) %>%
  left_join(model_data_actr %>%
              mutate(obs_id = row_number()) %>%
              select(obs_id, pp_num, fan_loc, fan_pers, fan_target, fan_word),
            by = "obs_id")

pred_long_actr %>% group_by(fan_target) %>% summarise(mean(rt_pred), sd(rt_pred))

ggplot() +
  geom_density(data = pred_long_actr %>% mutate(source = paste0("pred_", fan_target)),
               aes(x = rt_pred, group = interaction(draw, fan_target), color = source), alpha = 0.3) +
  geom_density(data = model_data_actr %>% mutate(source = paste0("obs_", fan_target)),
               aes(x = rt, color = source), linewidth = 1) +
  scale_color_manual(values = c("obs_-1" = "darkblue", "pred_-1" = "lightblue",
                                "obs_1"  = "darkred",  "pred_1"  = "lightcoral"),
                     labels = c("obs_-1" = "observed fan 2", "pred_-1" = "predicted fan 2",
                                "obs_1"  = "observed fan 4", "pred_1"  = "predicted fan 4")) +
  guides(color = guide_legend(
    override.aes = list(
      fill = c("darkblue", "darkred", "lightblue", "lightcoral"),
      linewidth = 0,
      alpha = 1
    ))) +
  scale_x_continuous(limits = c(200, 6000)) +
  labs(x = "RT (ms)", color = NULL) +
  theme_bw(30) +
  theme(legend.position = c(0.75, 0.75))

ggsave("../figures/ppc-actr_model.png", width=10, height=7)


boxplot_data <- bind_rows(
  pred_long_actr %>%
    mutate(fan_target = factor(fan_target, levels = c(-1, 1), labels = c("fan 2", "fan 4"))) %>%
    select(rt = rt_pred, fan_target) %>% mutate(type = "predicted"),
  model_data_actr %>%
    mutate(fan_target = factor(fan_target, levels = c(-1, 1), labels = c("fan 2", "fan 4"))) %>%
    select(rt, fan_target) %>% mutate(type = "observed")
)

ggplot(boxplot_data, aes(x = fan_target, y = rt, fill = interaction(type, fan_target))) +
  geom_boxplot(position = position_dodge(0.8)) +
  scale_fill_manual(values = c("observed.fan 2"  = "darkblue",  "predicted.fan 2" = "lightblue",
                                "observed.fan 4"  = "darkred",   "predicted.fan 4" = "lightcoral"),
                    labels = c("observed.fan 2"  = "observed fan 2",  "predicted.fan 2" = "predicted fan 2",
                               "observed.fan 4"  = "observed fan 4",  "predicted.fan 4" = "predicted fan 4")) +
  scale_y_log10(limits = c(200, 6000)) +
  labs(x = NULL, y = "RT (ms)", fill = NULL) +
  theme_bw(30) +
  theme(legend.position = c(0.85, 0.85))

ggsave("../figures/boxplot-actr_model.png", width=10, height=7)

```

One quantile plot. We are not using these. They are a bit hard to make sense of (we take mean for rt_pred, so there are no individual observations here).

```{r}
qbin_assignment <- model_data_actr %>%
  mutate(obs_id = row_number(), quantile_bin = ntile(rt, 5)) %>%
  select(obs_id, quantile_bin)

obs_quant <- model_data_actr %>%
  mutate(quantile_bin = ntile(rt, 5), fan_target = as.factor(fan_target)) %>%
  group_by(fan_target, quantile_bin) %>%
  summarise(rt = mean(rt), .groups = "drop")

pred_quant <- pred_long_actr %>%
  left_join(qbin_assignment, by = "obs_id") %>%
  mutate(fan_target = as.factor(fan_target)) %>%
  group_by(fan_target, quantile_bin, draw) %>%
  summarise(rt = mean(rt_pred), .groups = "drop")

ggplot() +
  geom_boxplot(data = pred_quant,
               aes(x = quantile_bin, y = rt, group = interaction(quantile_bin, fan_target), fill = fan_target),
               alpha = 0.5, color = NA) +
  geom_line(data  = obs_quant, aes(x = quantile_bin, y = rt, color = fan_target)) +
  geom_point(data = obs_quant, aes(x = quantile_bin, y = rt, color = fan_target), size = 3) +
  scale_fill_manual(values  = c("-1" = "lightblue",  "1" = "lightcoral"),
                    labels  = c("-1" = "predicted fan 2", "1" = "predicted fan 4")) +
  scale_color_manual(values = c("-1" = "darkblue",   "1" = "darkred"),
                     labels = c("-1" = "observed fan 2",  "1" = "observed fan 4")) +
  scale_y_log10() +
  labs(x = "Quantile bin", y = "Mean RT (ms)", fill = NULL, color = NULL) +
  theme_bw(30) +
  theme(legend.position = c(0.2, 0.8))

ggsave("../figures/quantiles-actr_model.png", width=10, height=7)
```
